>

### 2025-03-17 docs/article.qmd
Restructure the discussion

This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics. By examining co-prescription patterns, we aimed to understand the nature of polypharmacy within these groups. The rate of polypharmacy differs between these two groups. While same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics, multi-class polypharmacy predominates among those treated with anxiolytics. In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy. The high occurrence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the occurrence of psychopharmaca polypharmacy [@de2004polypharmacy]. This highlights the interconnected nature of psychopharmaca prescription patterns.

To better understand these co-prescription patterns, the DPN was constructed to identify medication classes with strong centralities in relation to antidepressants and anxiolytics. Following @Cavallo2012, the weight of the adjacency matrix was the frequency of co-prescriptions or single prescriptions. We adjusted the weight to account for varying prescription dosages, alleviating previous limitation where the DDD was restricted to 1 [@Cavallo2012]. Seven medication classes clustered together, forming a modular structure. This modularity reflects the organization of medications into anatomically or functionally related groups, where certain drugs were found to form densely interconnected nodes preferentially linked to each other [@Bazzoni2015]. These network properties highlight the utility of DPNs in revealing prescribing patterns and their underlying clinical rationale.

Seven medication classes were identified with a high eigenvector centrality in our DPN. Unsurprisingly, antidepressants and anxiolytics exhibited high centrality, as these medication classes were central to our DPN. Beyond these, medication classes with high centrality included those for the alimentary tract and metabolism (WHO ATC code `A`), blood and blood-forming organs (code `B`), cardiovascular system (code `C`), respiratory system (code `R`), and analgesics (code `N02`). These classes are closely associated with chronic illnesses. This finding aligns with previous investigation highlighting the bidirectional associations between depression/anxiety and chronic physical illnesses [@qi2024longitudinal]. For instance, a study demonstrated that diabetes mellitus, thyroid disorders, and asthma increased the risk of depression [@jang2024temporal]. Moreover, these conditions often necessitate long-term pharmacological interventions, increasing the likelihood of co-prescription. Similarly, fears of worsening symptoms in chronic diseases can lead to heightened health-related anxiety [@lebel2020health]. The frequent coexistence of physical and mental health conditions in chronic diseases underscores the rationale for polypharmacy regimens [@nizamie2015rational].

We acknowledge several limitations in this study. First, data aggregation at the population level resulted in the loss of individual-level information, limiting interpretation to population trends. Second, while the adjustment of weights based on DDD introduces a novel element to the analysis, it is important to note that DDD values are not always equal to one, as defined by the WHO ATC system. However, our approach aligns with the general recommendation of @Cavallo2012, where DDD of 1 forms the basic of network edges. The adjusted weighting penalizes values deviating significantly from 1, reducing their impact on the network. Future studies should explore alternative weighting methods to further refine the analysis.

Despite the limitations, our study demonstrates the utility of DPN as a powerful, data-driven approach to analyzing prescription dispensing data. By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering deeper insights into prescribing behaviors. These insights can reveal important trends in medication use, which can be essential to public health monitoring. By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts

@@

This study utilized DPN to evaluate the influence of specific medication classes on prescribing patterns of antidepressants and anxiolytics. By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens. This study highlights the potential of network-based approaches to narrow down high-impact medications for further evaluation.

>>>>

This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct polypharmacy patterns between these groups. While same-class polypharmacy was more common among antidepressant users, multi-class polypharmacy predominated among those receiving anxiolytics. Notably, in both groups, multi-class polypharmacy was at least ten times more prevalent than same-class polypharmacy. Seven medication classes exhibited high eigenvector centrality, indicating their strong influence on co-prescription dynamics. These include medications for the alimentary tract and metabolism (ATC code `A`), blood and blood-forming organs (`B`), cardiovascular system (`C`), respiratory system (`R`), and analgesics (`N02`). These classes do not merely appear frequently but also serve as key connectors within prescribing networks, linking psychiatric treatments to chronic disease management. Their centrality suggests that they play a role in structuring multi-class polypharmacy, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities.

Our findings align with previous research showing that antidepressants and anxiolytics are frequently co-prescribed with other medications [@Shrivastava2013], and that multi-class regimens contribute most to psychopharmaca polypharmacy [@de2004polypharmacy]. Furthermore, there have been established bidirectional associations between depression/anxiety and chronic illnesses [@qi2024longitudinal]. Conditions such as diabetes mellitus, thyroid disorders, and asthma have been linked to an increased risk of depression [@jang2024temporal]. The need for long-term pharmacological management further drives co-prescription patterns. Additionally, chronic illness-related anxiety can contribute to heightened prescribing of anxiolytics [@lebel2020health]. This underscores the interconnected nature of psychopharmaca prescribing patterns and highlights the complexity of medication management in these populations.

DPN complements traditional drug utilization analyses by capturing the structural properties of prescribing behaviors. Beyond evaluating individual drug utilization or basic pairwise co-prescriptions, DPN provides a structural perspective by mapping the interconnections between medications within a broader prescribing network [@Bazzoni2015]. The network approach is a particularly useful method for understanding complex prescribing dynamics, which allows for the identification of central medication classes that influence polypharmacy patterns. The high centrality of certain medication classes suggests they serve as critical connectors in treatment regimens, providing the basis for further monitoring and evaluation.

By mapping the relationships between medications, DPN enables the detection of patterns that would be challenging to observe through standard statistical methods. For instance, the high centrality of certain medication classes suggests that they play a pivotal role in multi-class polypharmacy, likely due to their involvement in managing both psychiatric and non-psychiatric conditions. As such, network analysis is a suitable approach for generating hypothesis, which has also been thoroughly discussed by @Askar2021.

We acknowledge several limitations in this study. First, data aggregation at the population level resulted in the loss of individual-level information, limiting interpretation to population trends. Second, while the adjustment of weights based on DDD introduces a novel element to the analysis, it is important to note that DDD values are not always equal to one, as defined by the WHO ATC system. Our study adopted a DDD-based weighting approach to refine network edges, aligning with the recommendation of @Cavallo2012. The adjusted weighting penalizes values deviating significantly from 1, reducing their impact on the network. Future research should explore alternative weighting techniques, such as patient-level dosage adjustments, to enhance network precision.

Despite the limitations, our study demonstrates the utility of DPN as a powerful, data-driven approach to analyzing medication dispensing data. By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering insights into prescribing behaviors. These insights can reveal important trends in medication use, which can be useful to public health monitoring. By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts.

Future DPN studies on individuals using antidepressants or anxiolytics should adopt a more fine-grained ATC classification to identify specific medications driving polypharmacy patterns within the currently identified seven medication classes. A more granular approach could reveal whether certain drugs disproportionately contribute to multi-class polypharmacy and whether these prescribing trends vary across patient demographics or healthcare settings. Such insights could refine our understanding of prescribing behaviors and inform targeted interventions for optimizing medication regimens.

::: {.content-hidden}
- Following @Cavallo2012, the weight of the adjacency matrix was the frequency of co-prescriptions or single prescriptions. We adjusted the weight to account for varying prescription dosages, alleviating previous limitation where the DDD was restricted to 1 [@Cavallo2012].
- Additionally, the predominance of multi-class polypharmacy in individuals using antidepressants or anxiolytics suggests the need for a more integrated approach to managing patients receiving psychotropic medications, ensuring that treatment decisions account for both psychiatric and non-psychiatric conditions.
:::

@@

This study utilized DPN to evaluate the influence of specific medication classes on prescribing patterns of antidepressants and anxiolytics. By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens for individuals using anxiolytics and antidepressants. This study highlights the potential of network-based approaches to narrow down high-impact medications for further evaluation.
